Body size patterns

### 2019-07-15 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
added figures for MS

# by species, by cohort gridded
# ggplot(vB %>% filter(cohort %in% 2000:2013), aes(ydayCumul,observedLength, group = species, color = (species))) +
#   geom_point(size = 0.5, alpha = 0.1) +
#  # geom_smooth(span = 0.1, size = 1.5, se = F) +
#   geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
#   facet_wrap( ~ cohort) +
#   theme_publication()

# by species (bkt, bnt), by cohort, by river gridded
ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength, group = species, color = (species))) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
  geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  facet_grid(riverOrdered ~ cohort) +
  theme_publication()
```

@@

summary(modBKT)
plot(modBKT, pages = 8, scale = 0)

predGridBKT <- expand.grid(riverFactor = unique(modBKT$model$riverFactor), 
                           cohortFactor = unique(modBKT$model$cohort),
                           ydayCumul = seq(250,1000, by = 30),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

summary(modBNT)
#plot(modBNT, pages = 8, scale = 0)

predGridBNT <- expand.grid(riverFactor = unique(modBNT$model$riverFactor), 
                           cohortFactor = unique(modBNT$model$cohort),
                           ydayCumul = seq(250,1000, by = 30),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

ggsave('./figures/predLengths.png', width = 11, height = 11, units='in')

# specific splines by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaled)', xAxisLab = 'Cohort Strength'))

#
plot.gam(modBKT, pages = 10)

>>>>

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength)) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
 # geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  labs(y = 'Observed body size (mm)',
       x = 'Days since age-0 Jan 1') +
  facet_wrap(~ speciesGG) +
  theme_publication()

ggsave('./figures/rawBySpecies.png', width = 11, height = 8, units='in')

# by species (bkt, bnt), by cohort, by river gridded
ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength, group = species, color = (species))) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
  geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  facet_wrap( ~ cohort) +
  theme_publication()

# by species (bkt, bnt), by cohort, by river gridded
ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength, group = species, color = (species))) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
  geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  facet_grid(riverOrdered ~ cohort) +
  theme_publication()

```{r rivers where fish are fish}

vB$riverGG <- factor(vB$riverFactor,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"))

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats'), !is.na(observedLength)),
       aes(riverGG, fill = speciesGG)) +
  geom_bar() +
  labs(x = 'River', y = 'Number of observations', fill = 'Species') +
  theme_publication() +
  scale_fill_grey() +
  theme(legend.position = "right", 
    legend.direction = "vertical",
    legend.title = element_text(face = "plain"))

ggsave('./figures/rawCountsBySpecies.png', width = 11, height = 8, units='in')

@@

summary(modBKT)
#plot(modBKT, pages = 8, scale = 0)

predGridBKT <- expand.grid(riverFactor = unique(modBKT$model$riverFactor), 
                           cohortFactor = unique(modBKT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

summary(modBNT)
#plot(modBNT,  scale = 0)

predGridBNT <- expand.grid(riverFactor = unique(modBNT$model$riverFactor), 
                           cohortFactor = unique(modBNT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

@@

ggsave('./figures/predLengths14.png', width = 11, height = 8, units='in')

# specific spline effects by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
ggsave('./figures/cohortEffect.png', width = 11, height = 8, units='in')
(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaled)', xAxisLab = 'Cohort Strength'))
ggsave('./figures/cohortStrengthEffect.png', width = 11, height = 8, units='in')
#
plot.gam(modBKT, pages = 10)

# plot specific predictions

# across rivers, by species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaled == 0, cohort == 2006, cohortStrengthScaled == 0),
       aes(ydayCumul, pred, group = speciesGG, color = speciesGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
#  scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_wrap(~ riverGG)

ggsave('./figures/ydayCumulAcrossRiverBySpp.png', width = 11, height = 8, units='in')

# across species, by rivers
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaled == 0, cohort == 2006, cohortStrengthScaled == 0),
       aes(ydayCumul, pred, group = riverGG, color = riverGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'River') +
  #scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_grid(~ speciesGG)

ggsave('./figures/ydayCumulAcrossSppByRiver.png', width = 11, height = 8, units='in')
